---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sovatools

<!-- badges: start -->
[![R-CMD-check](https://github.com/kelly-sovacool/sovatools/workflows/R-CMD-check/badge.svg)](https://github.com/kelly-sovacool/sovatools/actions)
[![Codecov test coverage](https://codecov.io/gh/kelly-sovacool/sovatools/branch/main/graph/badge.svg)](https://app.codecov.io/gh/kelly-sovacool/sovatools?branch=main)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

```{r desc, results = 'asis', message = FALSE, warning = FALSE}
library(dplyr)
cat(stringr::str_replace_all(utils::packageDescription('sovatools')['Description'],
                             '\n', ' '))
```


## Installation

You can install the development version of sovatools from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kelly-sovacool/sovatools")
```

## Help & Contributing

If you come across a bug, 
[open an issue](https://github.com/kelly-sovacool/sovatools/issues) 
and include a 
[minimal reproducible example](https://www.tidyverse.org/help/).

If you have questions, create a new post in 
[Discussions](https://github.com/kelly-sovacool/sovatools/discussions).

If you'd like to contribute, see our guidelines
[here](https://sovacool.dev/sovatools/CONTRIBUTING.html).

## About

The [overly-honest methods section](https://twitter.com/hashtag/overlyhonestmethods) 
would read that I thought of this package name before thinking of code to
include in it.
Mainly it is a collection of functions intended for [my](https://sovacool.dev) 
own use that don't have an obvious home in any of the other R packages I maintain.
If other people find this package useful, that's cool too!
